BERT Model Compression and Weight Sharing

### 2019-05-11 paper/paper.tex
Add more to KD section

\section{Model}

@@

>>>>

\section{Model}
\label{sec:model}

@@

The benefits of training in this fashion have been empirically documented
% TODO: paper on KD doing well?
and have theoretical motivation. Our goal of any network is to learn the
conditional distribution 
\[ p(y_i = k \mid \bm{x}_i).\]
In traditional training, we do this by observing the draws $y_i$ from this
distribution. However, to the extent that the teacher network prediction is a
good approximation of the true conditional distribution, the student network can
learn faster because it is being pushed toward predicting the de-noised
expectation.

To present a simplified example: if a neural network were trying to understand a
coin flip, it would require a number of observations of heads and tails to
conclude the underlying probability is 50\% toward either direction. However, if
it is directly shown that the probability was 50\% each time, regardless of what
the coin came up, it will in less time understand that the probability is always
50\%.

An additional benefit from knowledge distillation arises from BERT's
pre-training. Because BERT is pre-trained on large amounts of unstructured data,
it contains a powerful language model which likely would be impossible to learn
from the specific task's data-set. To an extent, relevant features from this
language model are what make BERT so powerful once it's fine-tuned. Training the
student network on BERT's output thus allows some of this ``outside knowledge''
to percolate toward the student network.

To provide a concrete example of how this might work, suppose BERT captures from
its pre-training that ``bad'', ``horrible,'' and ``terrible'' are approximate
synonyms. In a sentiment task, these three words appear in three different
sentences, two of which are negative, and one of which is positive. A fine-tuned
BERT may provide a lower likelihood of being positive to the positive sentence
than it would otherwise even if

% TODO: KD benefits

For our knowledge distillation, we make use of a fine-tuned BERT on a task as
our teacher network and train a simpler model to emulate the predictions use
\nameref{sec:model}
